---
title: "Course Project "
author: "Yi.LI"
date: "2019/5/7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 Import data & understanding data

1st Step: Import data & understanding data
Found that: 1) In training data, target "Classe" has 5 values, and 2) in testing data has no value (NA)

```{r import}
rm(list = ls (all = TRUE))
library(caret)
training = read.csv("C:/Users/e00637a/Desktop/Lorin/Self-development/R Machine Learning/pml-training.csv")
testing = read.csv("C:/Users/e00637a/Desktop/Lorin/Self-development/R Machine Learning/pml-testing.csv")
dim(training); dim(testing)
summary(training$classe); summary(testing$classe)
```


## 2 Split training Data into Tranining and Testing, leave testing as final test


```{r split}
set.seed(1039)
inTrain = createDataPartition(training$classe, p = 3/4)[[1]]
preTraining = training[ inTrain,]
preTesting = training[-inTrain,]
dim(preTraining); dim(preTesting)
```


## 3 Variables analysis
check the missing value and abnormal value rate for all variables, and exclude variables with missing rate or abnormal value rate >= 85%
Result: filter out 57 variables with high missing rate; filter out 33 variables with high abnormal rate; 

```{r analysis}
na_flag = apply(is.na(training), 2, sum)
trainingClean = preTraining[,which(na_flag <(14718*0.85) )]
dim(trainingClean)


## 2) Abnormal value
f = function(x) sum(x=="#DIV/0!", x=="")
an_flag = apply(trainingClean ,2,f)
trainingClean2 = trainingClean[,which(an_flag <(14718*0.85))]
dim(trainingClean2)

trainingDev = subset(trainingClean2,select=-c(X,user_name,cvtd_timestamp,new_window,classe))
dim(trainingDev)
```

## 4 PCA + RF 
Choose random forest as modelling methodology, but firstly conduct a PCA because there are still too many variables and may have high correlations
Model accuracy in testing data is: 0.9741

```{r modelling}
preProc =preProcess(trainingDev, method ="pca", thresh=0.80) 
trainPC =predict(preProc, trainingDev)
Dev = data.frame(subset(preTraining, select =classe), trainPC)
dim(Dev)
modelFit = train(classe~.,method ="rf", data=Dev)

dim(preTesting)
testPC = predict(preProc, preTesting[,c(names(trainingDev))])
Tes = data.frame(subset(preTesting, select=classe), testPC)
confusionMatrix(Tes$classe, predict(modelFit, Tes))
```



## 5 Apply on final testing Data (without classe value)
Prediction result in 20 test samples: B A B A A E D B A A B C B A E E A B B B  ##
```{r predict}
testFinal = predict(preProc, testing[,c(names(trainingDev))])
preResult = predict(modelFit, testFinal)
print(preResult)
```



